
---
title: "Assignment 1 - some R practice"
---

# A word about R markdown

The assignments for our online R training course will all take the form of R
markdown documents like this one. These are files ending in '.Rmd' that combine
R code blocks with plain text, such as this paragraph that you're reading now.

To run the R code blocks you need to have this R markdown file open in RStudio.
If you're reading this in RStudio right now then all is good and well. If not,
please start RStudio and open this file using the 'Open File...' option from the
'File' menu.

Also, save this to your personalFiles folder!!

In these assignments we will describe what we're asking you to do in some plain
text which will be followed by an empty code block in which you will write the
R commands as your answers to the exercise.

Here's an example. Suppose we ask you to add two numbers, 34 and 102, together.
The empty code block where you would carry out this calculation would look like
this:

```{r}

```

It should appear as a grey box with three small grey and green icons at the top
on the right hand side.

You can fill in the answer as follows:

```{r}
34 + 102
```

You can add extra lines as necessary by hitting the 'Return' key.

Now to run this command you can click on the green play icon, the
one that is furthest right and points right-ward. 

You should see the answer printed just below the code block, like your console.


# Using R as a calculator

1. Convert the following temperatures given in degrees Fahrenheit to Celsius:
45, 96, 451

```{r}

```

Hint: just do what you'd normally do if you can't remember the formula for
converting between Celsius and Fahrenheit (Google in my case).

2. Similarly, convert the following temperatures in degrees Celsius to
Fahrenheit: -65, 100, 20

```{r}

```

# Generating sequence vectors

3. Generate a sequence of numbers representing the days of a year called  `dayPerYr`

```{r}

```

Your friendly statistician has suggested that there should be an R
function to create a sequence.  Using this function (go look it up) create a sequence from 1 to 365 but now do it in 5 day intervals using the `by` parameter of this function. Call the new object `fiveDayWindows`

```{r}

```

# Looking at types of objects

4. Run the code below and use the class() function (check it's
help page) and see how R treats each newly-created vector?  After that run it again and use `typeof` to see if there are differences.

```{r}
num_char <- c(1, 2, 3, "a")
num_logical <- c(1, 2, 3, TRUE)
char_logical <- c("a", "b", "c", TRUE)
tricky <- c(1, 2, 3, "4")
```

R coerces the data to a lowest common denominator - it has an internal hierarchy.
Can you work out the hierarchy?

# Plotting data

Using base R, plot the counts (on the y-axis) by the days (x-axis).  While you're at it, look at the documentation for `?rnorm` to see that is does.

```{r}
days <- c(1, 2, 4, 6, 8, 12, 16)
counts <- days ^ 2 + rnorm(days, mean = days)

# add your code here

```

# Exploring and summarizing data

6. Your colleague has supplied you with the following table:

| Day | LineA | LineB | LineC |
| --- | ----- | ----- | ----- |
|  1  |    4  |    5  |   14  |
|  2  |    9  |   17  |   16  |
|  3  |    7  |   22  |   10  |
|  4  |   12  |   20  |   14  |
|  5  |   23  |   24  |   20  |
|  6  |    8  |   18  |   12  |

Create vectors for each column.  Then create a dataframe called `df` with all vectors.  Next, find summary statistics for the entire df object.  Try to build at least one plot from this table.  

```{r}

```

Now lets explore vector operations.
- Add a column to `df` called `BooleanVec` with values T,T,F,T,F,T
- Create a new column called `multiplyFour` which multiple `LineA` by 4.
- Plot the tally of the `BooleanVec` column.
- Table the `LineB` by  `BooleanVec`

```{r}

```

