
---
title: "Practice 2 - more coding"
---

---

### Working with vectors, data frames and tibbles

**1. How many cars in the `mtcars` data set have 8 cylinders?**

Write an R instruction to calculate this.

```{r}
data(mtcars)

```

**2. Print out a subset of the `mtcars` containing just Merc**

```{r}

```

**3. For the Mercedes cars, calculate ratio of hp by cyl, and round it to 2 places**

```{r}

```

---

### Simulation: rolling 6-sided dice

**4. Use the `sample()` function to simulate the rolling of a 6-sided die**

If you look at the help page for `sample` you'll find there are two functions
with the same name, one in the `base` package and the other in the `dplyr`
package. The `sample` function in the `base` package is the one you need for
this exercise.

Count the number of sixes you get for 1000 rolls?

```{r}

```

What number would you expect to get? Calculate this in R.

```{r}

```

Re-run the simulation a few times by clicking on the green 'Run current chunk'
button for the code you've written. What do you notice?

Re-run the simulation with a much larger sample size. Check that the number of
sixes you obtain is much closer to the expected value.

```{r}

```

Now plot the density and histogram of outcomes from 1000 "rolls" of the die.

```{r}

```


**5. Simulate the rolling of a weighted six-sided die**

Imagine we're running a casino and we have some weighted dice in which the
probability of throwing a six is a bit lower than it should be if all is fair
and square. Let's say the probability of a throwing a six is 0.1 while the
other 5 numbers all have equal probability.

Calculate the probability for throwing each of the other numbers and then,
referring again at the help page for `sample()`, re-run the simulation using
these probabilities. See how many sixes you get.

```{r}

```
